The Local Group in the Cosmic Web

### 2014-08-13 paper/main.tex
typos corrected

\begin{abstract}
We explore the characteristics of the
cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The sample of LG counterparts is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed for the LG.  
The second is a subset with additional observed kinematic constaints 
such as relative pair velocity and separation. 
We find that the pairs in the LG sample with all constraints are: (i)
Preferentially   located in filaments and sheets, (ii) Located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
Applied to the observed LG, there is a potential conflict between
these alignments and recent claims of an universal subhalo accretion
direction. 
This highlights the relevance of achieving a precise characterization
of the place of the LG in the cosmic web in a the cosmological context
provided by $\Lambda$CDM.

@@

This combination of features makes LG analogues uncommon. 
Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error from current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters. 
A similar abundance was found by \cite{ForeroRomero2011} by comparing the
formation history of LG pairs in constrained simulations with the
results of unconstrained cosmological simulations.

\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not sufficiently rare to
challenge the \lcdm model.  
Another set of criteria for LG analogues was used
by \citet{2008MNRAS.384.1459L}, but despite differences in the
definitions and resulting fraction of LG analogues, results are in
agreement with a low pairs frequency aswell.

@@

Observationally, the LG is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group \citep{2013AJ....146...69C}.
At this scale, there is no evident alignment of the MW-M31 orbital
plane with any local filament or the Virgo-Fornax direction. However,
if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
a clear alignment of the MW-M31 orbit with a local plane of galaxies
as shown by Figure $3$ in \citet{2013AJ....146...69C}.

We can then ask, to what extent is this an expected configuration in
$\Lambda$CDM? In particular, which are the typical/prefered locations
of these systems within the Cosmic Web?

@@

\begin{equation}
T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
\end{equation}
%
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates and $\phi$ is the gravitational potential renormalized to
follow the Poisson equation $\nabla^2\phi=\delta$ where
$\delta$ is the matter overdensity.

@@

\cite{Tweb} performed a detailed study for the topology of the
cosmic web and its visual counterpart as a function of the parameter
$\lambda_{\rm th}$. 
They found that reasonable results in terms of the
volume fraction occupied by voids, the visual inspection and the halo
populations in each web type can be reached by values of $0.2<\lambda_{\rm
th}<0.4$. 
In this \manuscript we choose the value of $\lambda_{\rm
  th}=0.3$ to proceed with our analysis. 
This is only relevant to the classification of the simulation into web
elements. Other results are completeley independent of this
choice. Nevertheless we have checked that the main conclusions of this
work do not depend on the precise choice of $\lambda_{\rm th}$.

The algorithm to compute the potential is grid based. 
First we interpolate the mass into a cubic grid with a
Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel in order to reduce the grid influence in the computations that follow. 
Then we obtain the gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. 
In our case we have used a grid size and a gaussian smoothing with
two times larger as the typical separation between the two halos in the Local Group. 
The purpose of this choice is to have both halos in the pair a common
environment. 
In this \manuscript we use a grid spacing of $s=0.97$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. 
The scale for the gaussian smoothing uses the same value.

@@

We also measure the alignment of the LG halos with respect to the
cosmic web defined by their eigenvectors.
To this end we characterize each LG pair by two vectors. 
The first is $\hat{n}$, the axis along the orbital angular
momentum of the pair, normal to its orbital plane; the second is
$\hat{r}$, the vector that connects the halos in the pair which can be
related to the alignment of the radial velocities to the web.
We quantify the alignment using the absolute value of the cosinus of
the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
\hat{n}|$ or $\mu=|\hat{e}_i\cdot \hat{r}|$, where $i=1,2,3$.

@@

We also define two subsets of restricted samples (RS) more closely
related to the MW-M31  dynamics according to the tolerance in
additional constraints. 
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly.  
The number of pairs in each sample is $46$ and $120$ respectively,
notice we have less pairs than in \citet{lganalogues}, since
we removed pairs which are too close at $z=0$, i.e. their virial radii
overlap, also we removed a couple of pairs that merged or change their
mass more than $20\%$ at present time since they were detected at
$z<0.1$.

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\
General ($12.1<\log_{10} M_{\rm LG}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
(43.0) & 1 (0.1)\\
\hline\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environments for each
of the three samples presented in Section \ref{sec:lg_analogues}. 
In parethesis the same number as a percentage of the total population.
The last line in the table corresponds to the general sample with an
additional mass cut for the total pair mass.  
\label{table:web_type}}
\end{center}
\end{table*}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.31\textwidth]{fig2a.pdf}
  \includegraphics[width=0.32\textwidth]{fig2b.pdf}
  \includegraphics[width=0.32\textwidth]{fig2c.pdf}
\caption{Mass dependency of the average dark matter overdensity (left),
  web ellipticity (middle) and web absolute value prolateness (right) at the
  pair location. 
\label{fig:median_overdensity}}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig5.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal vector $\hat{n}$ and each one of the
  eigenvectors.  The lines show the trends for the general sample.
\label{fig:median_alignment_n}}
\end{center}
\end{figure}

@@

\subsection{The prefered environment for LGs}

The first result we explore is the kind of environment occupied by
our LGs, and use as reference sample the GS where pairs are much more
relaxed in mass and kinematic constraints.
We find that the pairs in the GS are located across all different
evironment without any strong preferences; $1/3$  are located in
sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning $1/6$ in
voids.

@@

We find that the difference between the GS and the RS 
can be explained by the total pair mass.
In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
amples is very narrow and it is used to constraint the LG mass.
We show in Table \ref{table:web_type} that a subset of the GS
having a similar mass range than the RS reproduces similar environment
fractions. The correlation betwen halo mass and their environment is a
well known result \citep{1998ApJ...500...14L}.

@@

Figure \ref{fig:median_overdensity} shows the dependency of these three
characteristics  on the total pair mass for the different samples.
GS is represented by the solid lines with the associated 
errors covered by the shaded region. 
The symbols represents the results for the $2\sigma$ and $3\sigma$
samples.   
In thre three cases it is evident that the range of values for the
$2\sigma$ and $3\sigma$ samples are completely expected from the mass
constraint alone.

@@

\subsection{Alignments withthe cosmic web}

@@

There are two important features in Figure \ref{fig:alignment_n}.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the second eigenvector the distribution is consistent
with no aligment. 
While for the first eigenvector there is a strong alignment, an expected
result considering the results with the other eigenvectors and
keeping in mind that they are orthonormal.
Second, the alignment strenght changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strenghtens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

@@

In the GS we already see an anti-alignment signature with the third eigenvector,
lower than for RS samples but still significant, this is an expected result,
even for random pairs with separations of the same order of the scale-lenght of 
underlying environment, just because individual pair members are more likely to lie 
following the density distribution. For instance, in a filamentary density distribution, random 
pairs are more likely to lie along the filament; and in walls, random pairs are more likely
to lie in the wall.

@@

We also explored the main orbit differences between the GS and RS  which could be
responsible of this alignment strength feature, and we have that RS samples contraint
the tangential velocity, then pair orbits are more eccentric as we tighten pair
constraints, and for GS sample there is no tangential velocity constraint at all.
Therefore, to study any relation between orbit eccentricity and alignment, we 
computed for each halo pair in all samples, an approximate orbit 
eccentricity assuming a two body orbit with masses set as the virial 
masses and initial conditions given by current velocity vector and separation.
We found that eccentricity is not responsible for this alignement feature by
selecting a subsample of GS having the same eccentricity than 
2$\sigma$-3$\sigma$ samples where we found no increase in the alignment when
compared with the full GS.

@@

We also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. 
Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($<36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|>0.95$ ($<18$ degrees angle). Similar to the previous case of
the $\hat{n}$ vector, the increasing strenght of the
$\hat{r}$ alignment cannot be explained by a selection on mass.

@@

In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$
($|\mu|=0.5$) and the angles between spins and orbital angular
momentum are $\sim33^{\circ}$ ($|\mu|=0.83$) and $\sim76^{\circ}$
($|\mu|=0.24$) for MW and M31 respectively
\citep{2012ApJ...753....9V}. 
This is consistent with our results of no strong alignement.

@@

This apparent contradition can be solved if one considers that the
subhalo infall properties depend on the environment at {\it the
  merger time}, while the alignments for yet unvirialized pairs such as the LG
depend on the current state of the cosmic web. This also explain the absence
of a strong alignment with halo spin, because it reflects past
configurations of the web, not the current one. From this perspective,
a joint consideration of the alignments between the dominant
halos in the LG and their satellites, which also feature strong
signals \citep{2005A&A...431..517K,2013ApJ...766..120C}, should
inform us about the structural evolution of the cosmic web.

Our results also raise the need to observationally constraint
the alignments of LG pairs with their cosmic web environment. To this end
one could use mass reconstructions from large surveys
\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S}
to select a LG sample to quantify the alignments with the filamentary
structure. 
This allows not only a direct quantification of how common are the LG
aligments but also provides a new test of $\Lambda$CDM.

>>>>

\begin{abstract}
We explore the characteristics of the
cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The sample of LG counterparts is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed for the LG.  
The second is a subset with additional observed kinematic constraints 
such as relative pair velocity and separation. 
We find that the pairs in the LG sample with all constraints are: (i)
Preferentially   located in filaments and sheets, (ii) Located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
Applied to the observed LG, there is a potential conflict between
these alignments and the evidence for satellite accretion along
filaments. 
This highlights the relevance of achieving a precise characterization
of the place of the LG in the cosmic web in the cosmological context
provided by $\Lambda$CDM.

@@

This combination of features makes LG analogues uncommon. 
Using numerical simulations \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error from current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters. 
A similar abundance was found by \cite{ForeroRomero2011} by comparing the
formation history of LG pairs in constrained simulations with the
results of unconstrained cosmological simulations.

\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not sufficiently rare to
challenge the \lcdm model.  
Another set of criteria for LG analogues was used
by \citet{2008MNRAS.384.1459L}, but despite differences in the
definitions and resulting fraction of LG analogues, results are in
agreement with a low pairs frequency as well.

@@

Observationally, the LG is located in a diffuse and
warped filament/wall connecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group \citep{2013AJ....146...69C}.
At this scale, there is no evident alignment of the MW-M31 orbital
plane with any local filament or the Virgo-Fornax direction. However,
if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
a clear alignment of the MW-M31 orbit with a local plane of galaxies
as shown by Figure $3$ in \citet{2013AJ....146...69C}.

We can then ask, to what extent is this an expected configuration in
$\Lambda$CDM? In particular, which are the typical/preferred locations
of these systems within the Cosmic Web?

@@

\begin{equation}
T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
\end{equation}
%
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordinates and $\phi$ is the gravitational potential renormalized to
follow the Poisson equation $\nabla^2\phi=\delta$ where
$\delta$ is the matter overdensity.

@@

\cite{Tweb} performed a detailed study for the topology of the
cosmic web and its visual counterpart as a function of the parameter
$\lambda_{\rm th}$. 
They found that reasonable results in terms of the
volume fraction occupied by voids, the visual inspection and the halo
populations in each web type can be reached by values of $0.2<\lambda_{\rm
th}<0.4$. 
In this \manuscript we choose the value of $\lambda_{\rm
  th}=0.3$ to proceed with our analysis. 
This is only relevant to the classification of the simulation into web
elements. Other results are completely independent of this
choice. Nevertheless we have checked that the main conclusions of this
work do not depend on the precise choice of $\lambda_{\rm th}$.

The algorithm to compute the potential is grid based. 
First we interpolate the mass into a cubic grid with a
Cloud-In-Cell (CIC) scheme and smooth it with a Gaussian kernel in order to reduce the grid influence in the computations that follow. 
Then we obtain the gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. 
In our case we have used a grid size and a Gaussian smoothing with
two times larger as the typical separation between the two halos in the Local Group. 
The purpose of this choice is to have both halos in the pair a common
environment. 
In this \manuscript we use a grid spacing of $s=0.97$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. 
The scale for the Gaussian smoothing uses the same value.

@@

We also measure the alignment of the LG halos with respect to the
cosmic web defined by their eigenvectors.
To this end we characterize each LG pair by two vectors. 
The first is $\hat{n}$, the axis along the orbital angular
momentum of the pair, normal to its orbital plane; the second is
$\hat{r}$, the vector that connects the halos in the pair which can be
related to the alignment of the radial velocities to the web.
We quantify the alignment using the absolute value of the cosine of
the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
\hat{n}|$ or $\mu=|\hat{e}_i\cdot \hat{r}|$, where $i=1,2,3$.

@@

We also define two subsets of restricted samples (RS) more closely
related to the MW-M31  dynamics according to the tolerance in
additional constraints. 
A sample named $2\sigma$, corresponding to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly.  
The number of pairs in each sample is $46$ and $120$ respectively,
notice we have less pairs than in \citet{lganalogues}, since
we removed pairs which are too close at $z=0$, i.e. their virial radii
overlap, also we removed a couple of pairs that merged or change their
mass more than $20\%$ at present time since they were detected at
$z<0.1$.

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\
General ($12.1<\log_{10} M_{\rm LG}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
(43.0) & 1 (0.1)\\
\hline\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environments for each
of the three samples presented in Section \ref{sec:lg_analogues}. 
In parenthesis the same number as a percentage of the total population.
The last line in the table corresponds to the general sample with an
additional mass cut for the total pair mass.  
\label{table:web_type}}
\end{center}
\end{table*}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.31\textwidth]{fig2a.pdf}
  \includegraphics[width=0.32\textwidth]{fig2b.pdf}
  \includegraphics[width=0.32\textwidth]{fig2c.pdf}
\caption{Mass dependency of the average dark matter overdensity (left),
  web ellipticity (middle) and web absolute value prolateness (right) at the
  pair location. The shaded contours indicate the $68\%$ confidence region. 
\label{fig:median_overdensity}}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig5.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal vector $\hat{n}$ and each one of the
  eigenvectors.  The lines show the trends for the general sample.
The error bars in the 2$\sigma$ and 3$\sigma$ points
  correspond to jackknife estimates. 
\label{fig:median_alignment_n}}
\end{center}
\end{figure}

@@

\subsection{The preferred environment for LGs}

The first result we explore is the kind of environment occupied by
our LGs, and use as reference sample the GS where pairs are much more
relaxed in mass and kinematic constraints.
We find that the pairs in the GS are located across all different
evironment without any strong preferences; $1/3$  are located in
sheets, $1/4$ in peaks, $1/4$ in filaments and the remaining $1/6$ in
voids.

@@

We find that the difference between the GS and the RS 
can be explained by the total pair mass.
In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
samples is very narrow and it is used to constraint the LG mass.
We show in Table \ref{table:web_type} that a subset of the GS
having a similar mass range than the RS reproduces similar environment
fractions. The correlation between halo mass and their environment is a
well known result \citep{1998ApJ...500...14L}.

@@

Figure \ref{fig:median_overdensity} shows the dependency of these three
characteristics  on the total pair mass for the different samples.
GS is represented by the solid lines with the associated 
errors covered by the shaded region. 
The symbols represents the results for the $2\sigma$ and $3\sigma$
samples.   
In the three cases it is evident that the range of values for the
$2\sigma$ and $3\sigma$ samples are completely expected from the mass
constraint alone.

@@

\subsection{Alignments with the cosmic web}

@@

There are two important features in Figure \ref{fig:alignment_n}.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the second eigenvector the distribution is consistent
with no alignment. 
While for the first eigenvector there is a strong alignment, an expected
result considering the results with the other eigenvectors and
keeping in mind that they are orthonormal.
Second, the alignment strength changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strengthens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

@@

In the GS we already see an anti-alignment signature with the third eigenvector,
lower than for RS samples but still significant, this is an expected result,
even for random pairs with separations of the same order of the scale-length of 
underlying environment, just because individual pair members are more likely to lie 
following the density distribution. For instance, in a filamentary density distribution, random 
pairs are more likely to lie along the filament; and in walls, random pairs are more likely
to lie in the wall.

@@

We also explored the main orbit differences between the GS and RS  which could be
responsible of this alignment strength feature, and we have that RS samples constraints
the tangential velocity, then pair orbits are more eccentric as we tighten pair
constraints, and for GS sample there is no tangential velocity constraint at all.
Therefore, to study any relation between orbit eccentricity and alignment, we 
computed for each halo pair in all samples, an approximate orbit 
eccentricity assuming a two body orbit with masses set as the virial 
masses and initial conditions given by current velocity vector and separation.
We found that eccentricity is not responsible for this alignment feature by
selecting a subsample of GS having the same eccentricity than 
2$\sigma$-3$\sigma$ samples where we found no increase in the alignment when
compared with the full GS.

@@

We also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. 
Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($<36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|>0.95$ ($<18$ degrees angle). Similar to the previous case of
the $\hat{n}$ vector, the increasing strength of the
$\hat{r}$ alignment cannot be explained by a selection on mass.

@@

In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$
($|\mu|=0.5$) and the angles between spins and orbital angular
momentum are $\sim33^{\circ}$ ($|\mu|=0.83$) and $\sim76^{\circ}$
($|\mu|=0.24$) for MW and M31 respectively
\citep{2012ApJ...753....9V}. 
This is consistent with our results of no strong alignment.

@@

This apparent contradiction can be solved if one considers that the
subhalo infall properties depend on the environment at {\it the
  merger time}, while the alignments for yet unvirialized pairs such as the LG
depend on the current state of the cosmic web. This also explain the absence
of a strong alignment with halo spin, because it reflects past
configurations of the web, not the current one. From this perspective,
a joint consideration of the alignments between the dominant
halos in the LG and their satellites, which also feature strong
signals \citep{2005A&A...431..517K,2013ApJ...766..120C}, should
inform us about the structural evolution of the cosmic web around the
LG.

Our results also raise the need to observationally constraint
the alignments of LG pairs with their cosmic web environment. To this end
one could use mass reconstructions from large surveys
\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S}
to select a LG sample to quantify the alignments with the filamentary
structure. 
This allows not only a direct quantification of how common are the LG
alignments but also provides a new test of $\Lambda$CDM.
